Representation Learning for Generalized Planning - SAT Encodings

### 2021-05-07 doc/paper/paper.tex
minor change
minor fix to the encoding

\paragraph{Bullet points}
\begin{itemize}
\item Learning generalized policies in unsupervised FOND domains from small examples.
\item FOND encoding, introducing Good(s, a) features to deal with non-determinism. Where $a \in A$, and $A$ is not required to be fixed. However, if $A$ is fixed we show a way to exploit it, reducing the number of transitions to distinguish.
\item Being complete in domains where not all states have a good transition, with the optional constraint Bad(s).
\item Empirical results with five domains: Chase, Shoot, Space Invaders, Delivery, Wumpus world.
\item Incremental policy learning, to address the scalability problem. First a random sample is taken from the whole graph and the policy is then refined incrementally by iteratively increasing the sample size. The strategy for increasing the size of the sample can be goal-directed or random.
%\item Introducing the sort of novelty to choose between the different successors classified as good by our policy
\item Use of a uniform grammar for the different grid domains.
\end{itemize}

@@

\smallpar{C8}
Good pairs $(s, a)$ implies at least one transition $(s, a, s')$ labeled as good.
\begin{align}
\bigvee_{s' \text{ s.t. } (s, a, s') \in T \setminus \badtx} Good(s, a, s'),&\;\; \text{for $(s, a)$ where $s$ alive.}
\end{align}

>>>>

\paragraph{Bullet points}
\begin{itemize}
\item Learning generalized policies in unsupervised FOND domains from small examples.
\item FOND encoding, introducing Good(s, a) features to deal with non-determinism. Where $a \in A$, and $A$ is not required to be fixed. However, if $A$ is fixed we show a way to exploit it reducing the number of transitions to distinguish.
\item Being complete in domains where not all states have a good transition, with the optional constraint Bad(s).
\item Empirical results with five domains: Chase, Shoot, Space Invaders, Delivery, Wumpus world.
\item Incremental policy learning, to address the scalability problem. First a random sample is taken from the whole graph and the policy is then refined incrementally by iteratively increasing the sample size. The strategy for increasing the size of the sample can be goal-directed or random.
%\item Introducing the sort of novelty to choose between the different successors classified as good by our policy
\item Use of a uniform grammar for the different grid domains.
\end{itemize}

@@

\smallpar{C8}
If $(s, a)$ is good, then the resulting transitions must be good too:
%(s, a, s') \in T \setminus \badtx
\begin{align}
Good(s, a) \rightarrow Good(s, a, s'),\;\; \text{for $(s, a, s') \in T$ where $s$ alive.}
\end{align}
